

#Setup and Data Import

```{r}
rm(list = ls())

library(dplyr)
library(ggplot2)
library(gglasso)
library(pracma)
library(tidyr)
library(fastDummies)
library(lemon)

#Data separated for storage on GitHub repository
df1 <- read.csv(file = "testmybrain_data_30Dec2022_part_1.csv")
df2 <- read.csv(file = "testmybrain_data_30Dec2022_part_2.csv")
df3 <- read.csv(file = "testmybrain_data_30Dec2022_part_3.csv")
df4 <- read.csv(file = "testmybrain_data_30Dec2022_part_4.csv")
df5 <- read.csv(file = "testmybrain_data_30Dec2022_part_5.csv")
df6 <- read.csv(file = "testmybrain_data_30Dec2022_part_6.csv")

#Binding split data
raw.data<- do.call("rbind", list(df1, df2, df3, df4, df5, df6))
```


#Data filtering

```{r}

#Data from first-time participants selecting the shortest version of the task
ft.data <- raw.data %>%
  filter(repeat. == "First Time") %>%
  filter(gameIndex == "easy") %>%
  filter(TN < 90) %>%
  filter(numtar == 1) %>%
  mutate(mov_avg = movavg(HandFlip, 3, type = c('s'))) %>%
  mutate(variability = abs(mov_avg-HandFlip))

```


#Separating data by phase

```{r}

early.data <- ft.data %>% 
  filter(TN >= 31 & TN <=41) %>% # reaches early in adaptation
  group_by(Subject.ID) %>%
  dplyr::summarise(EA = mean(HandFlip, na.rm = TRUE))

late.data <- ft.data %>% 
  filter(TN >= 74 & TN <=84) %>% # reaches late in adaptation
  group_by(Subject.ID) %>%
  dplyr::summarise(LA = mean(HandFlip, na.rm = TRUE))

ae.data <- ft.data %>% 
  filter(TN >= 85 & TN <=90) %>% # reaches in after-effect phase
  group_by(Subject.ID) %>%
  dplyr::summarise(AE = mean(HandFlip, na.rm = TRUE))

```


#Summarize demographic + behavioral vars

```{r}

demo.vars <- ft.data %>% filter(TN > 1 & TN <= 30) %>%
  group_by(Subject.ID,
           Age, 
           Sleep, 
           ComputerUsage,
           Handedness,
           education, 
           rating, 
           mousetype, 
           racialorigin, 
           sex, 
           vision, 
           clumsy, 
           videogames, 
           major,
           browsertype,
           screensize,
           cardinal,
           CCW,
           NeuroDisease) %>%
  dplyr::summarise(RT_mean_baseline = mean(RT, na.rm = TRUE),   # reaction, movement, and start time over first 30 trials
                   MT_mean_baseline = mean(MT, na.rm = TRUE),
                   ST_mean_baseline = mean(ST, na.rm = TRUE),
                   Var_sum_baseline = sum(variability, na.rm = TRUE))   # variability in reach over first 30 trials

```


#Early phase data

```{r}

# Merging demographic and task data for Early phase
early.data.w.demo <- full_join(early.data,
                               demo.vars,
                               by = c("Subject.ID")) %>% drop_na()


# Converting categorical variables w/o clear hierarchy into dummy variables
early.data.w.dummy.demo <- dummy_cols(early.data.w.demo,
                                     select_columns = c("mousetype",
                                                        "sex",
                                                        "Handedness",
                                                        "racialorigin",
                                                        "major",
                                                        "browsertype"),
                                     remove_selected_columns = TRUE)

# Z-scoring continuous variables
early.data.w.dummy.demo.scaled <- na.omit(early.data.w.dummy.demo %>% 
                                                  mutate_at( c("EA",
                                                               "Age",
                                                               "Sleep",
                                                               "ComputerUsage",
                                                               "education",
                                                               "rating",
                                                               "clumsy",
                                                               "videogames",
                                                               "RT_mean_baseline",
                                                               "MT_mean_baseline",
                                                               "ST_mean_baseline",
                                                               "Var_sum_baseline",
                                                               "screensize"),
                                                             scale), by = "Subject.ID") %>%
  
  dplyr::rename(racialorigin_african_american = 'racialorigin_african-american', # renaming variables with special characters
                racialorigin_indian_native = 'racialorigin_indian/native',
                racialorigin_pacific_islander = 'racialorigin_pacific-islander')

```


#Late phase data

```{r}

# Merging demographic and task data for Late phase
late.data.w.demo <- full_join(late.data,  
                              demo.vars,
                              by = c("Subject.ID")) %>% drop_na()


# Converting categorical variables w/o clear hierarchy into dummy variables
late.data.w.dummy.demo <- dummy_cols(late.data.w.demo, 
                                     select_columns = c("mousetype",
                                                        "sex",
                                                        "Handedness",
                                                        "racialorigin",
                                                        "major",
                                                        "browsertype"),
                                     remove_selected_columns = TRUE)

# Z-scoring continuous variables
late.data.w.dummy.demo.scaled <- na.omit(late.data.w.dummy.demo %>% 
                                                  mutate_at( c("LA",
                                                               "Age",
                                                               "Sleep",
                                                               "ComputerUsage",
                                                               "education",
                                                               "rating",
                                                               "clumsy",
                                                               "videogames",
                                                               "RT_mean_baseline",
                                                               "MT_mean_baseline",
                                                               "ST_mean_baseline",
                                                               "Var_sum_baseline",
                                                               "screensize"),
                                                             scale), by = "Subject.ID") %>%
  
  dplyr::rename(racialorigin_african_american = 'racialorigin_african-american', # renaming variables with special characters
                racialorigin_indian_native = 'racialorigin_indian/native',
                racialorigin_pacific_islander = 'racialorigin_pacific-islander')

```


#Aftereffect phase data

```{r}

# Merging demographic and task data from aftereffect phase
ae.data.w.demo <- full_join(ae.data,
                            demo.vars,
                            by = c("Subject.ID")) %>% drop_na()

# Converting categorical variables w/o clear hierarchy into dummy variables
ae.data.w.dummy.demo <- dummy_cols(ae.data.w.demo, 
                                            select_columns = c("mousetype",
                                                               "sex",
                                                               "Handedness",
                                                               "racialorigin",
                                                               "major",
                                                               "browsertype"),
                                            remove_selected_columns = TRUE)

# Z-scoring continuous variables
ae.data.w.dummy.demo.scaled <- na.omit(ae.data.w.dummy.demo %>% 
                                                  mutate_at( c("AE",
                                                               "Age",
                                                               "Sleep",
                                                               "ComputerUsage",
                                                               "education",
                                                               "rating",
                                                               "clumsy",
                                                               "videogames",
                                                               "RT_mean_baseline",
                                                               "MT_mean_baseline",
                                                               "ST_mean_baseline",
                                                               "Var_sum_baseline",
                                                               "screensize"),
                                                             scale), by = "Subject.ID") %>%
  
  dplyr::rename(racialorigin_african_american = 'racialorigin_african-american',
                racialorigin_indian_native = 'racialorigin_indian/native',
                racialorigin_pacific_islander = 'racialorigin_pacific-islander') # renaming variables with special characters

```


#Group LASSO Regression on Early data

```{r}
set.seed(111)
early.lasso.data <- early.data.w.dummy.demo.scaled

# Find 80% of the sample
early.eighty.percent <- sample.int(n = nrow(early.lasso.data),        
                            size = floor(.8 * nrow(early.lasso.data)), 
                            replace = FALSE)

# 80% training data
early.training <- early.lasso.data[early.eighty.percent, ]    

# 20% test data to be held until last step
early.test <- early.lasso.data[-early.eighty.percent, ]   

# All predictors
early.x <- early.training %>% select(-starts_with("Subject.ID"), -EA) %>% data.matrix() 

# Early adaptation outcomes per subject
early.y <- early.training$EA  

# A list, supplied to cv.gglasso, designating which variables belong to the same group
groups <- c(rep(1:16, each = 1),   # First 16 columns should be treated as their own variables
            rep(17:17, each = 3),  # 3 mouse-type columns belong to the same group
            rep(18:18, each = 3),  # 3 sex columns belong to the same group
            rep(19:19, each = 3),  # 3 handedness columns belong to the same group
            rep(20:20, each = 8),  # 8 race columns belong to the same group
            rep(21:21, each = 6), # 6 major columns belong to the same group
            rep(22:22, each = 6)) # 6 browser columns belong to the same group

# Building the cross-validated group LASSO model on early adaptation data
early.cv.fit <- cv.gglasso(x = early.x,
                           y = early.y,    
                           group = groups,     # designate groups
                           pred.loss = "L2",   # least squares regression
                           loss = 'ls',        # deviation from the fitted mean to the response
                           nfolds = 10)        # ten-fold cross-validation

# Predicting held-out data using the model
early.pred.y <- predict(early.cv.fit$gglasso.fit,
                        newx = early.test %>% select(-starts_with("Subject.ID"), -EA) %>% data.matrix(),
                        s = early.cv.fit$lambda.min) # selecting minimum lambda 

# Calculating R-squared
early.sst <- sum((early.test$EA - mean(early.training$EA))^2)    # Sum of Squares Total
early.sse <- sum((early.pred.y - early.test$EA)^2)           # Sum of Squares Error
early.rsq <- 1 - early.sse / early.sst                       # R squared
early.rsq 

# Extracting the beta coefficients contained in the model
early.betas <- as.data.frame(as.matrix(coef(early.cv.fit,
                                            s = early.cv.fit$lambda.min))) %>% tibble::rownames_to_column("Feature")

# Correlation between predicted vs. actual
cor.test(early.test$EA, early.pred.y)

```


#Group LASSO Regression on Late data

```{r}
set.seed(123)
late.lasso.data <- late.data.w.dummy.demo.scaled

# Find 80% of the sample
late.eighty.percent <- sample.int(n = nrow(late.lasso.data),
                                  size = floor(.8 * nrow(late.lasso.data)),
                                  replace = FALSE)

# 80% Training data
late.training <- late.lasso.data[late.eighty.percent, ]    

# 20% Test data to be held until last step
late.test <- late.lasso.data[-late.eighty.percent, ]   

# All predictors
late.x <- late.training%>%select(-starts_with("Subject.ID"), -LA) %>% data.matrix()

# Late adaptation outcomes per subject
late.y <- late.training$LA

# Building the cross-validated group LASSO model on late adaptation data
late.cv.fit <- cv.gglasso(x=late.x,
                          y=late.y,
                          group=groups,      # designate groups
                          pred.loss = "L2",  # least squares regression
                          loss = 'ls',       # deviation from the fitted mean to the response
                          nfolds = 10)       # ten-fold cross-validation

# Predicting held-out data using the model
late.pred.y <- predict(late.cv.fit$gglasso.fit,
                       newx = late.test%>%select(-starts_with("Subject.ID"), -LA) %>% data.matrix(),
                       s = late.cv.fit$lambda.min) # selecting minimum lambda 

# Calculating R-squared
late.sst <- sum((late.test$LA - mean(late.training$LA))^2)    #Sum of Squares Total
late.sse <- sum((late.pred.y - late.test$LA)^2)           #Sum of Squares Error
late.rsq <- 1 - late.sse / late.sst                       #R squared
late.rsq 

# Extracting the beta coefficients contained in the model
late.betas <- as.data.frame(as.matrix(coef(late.cv.fit,
                                           s = late.cv.fit$lambda.min))) %>% tibble::rownames_to_column("Feature")

# Correlation between predicted vs. actual
cor.test(late.test$LA, late.pred.y)

```


#Group LASSO Regression on Aftereffect data

```{r}
set.seed(111)
ae.lasso.data <- ae.data.w.dummy.demo.scaled

# Find 80% of the sample
ae.eighty.percent <- sample.int(n = nrow(ae.lasso.data),
                                size = floor(.8 * nrow(ae.lasso.data)),
                                replace = FALSE)

# 80% Training data
ae.training <- ae.lasso.data[ae.eighty.percent, ] 

# 20% Test data to be held until last step
ae.test <- ae.lasso.data[-ae.eighty.percent, ]

# All predictors
ae.x <- ae.training%>%select(-starts_with("Subject.ID"), -AE) %>% data.matrix()

# Aftereffect outcomes per subject
ae.y <- ae.training$AE

# Building the cross-validated group LASSO model on aftereffect data
ae.cv.fit <- cv.gglasso(x=ae.x,
                        y=ae.y,
                        group=groups,       # designate groups
                        pred.loss = "L2",   # least squares regression
                        loss = 'ls',        # deviation from the fitted mean to the response
                        nfolds = 10)        # ten-fold cross-validation

# Predicting held-out data using the model
ae.pred.y <- predict(ae.cv.fit$gglasso.fit,
                     newx = ae.test%>%select(-starts_with("Subject.ID"), -AE) %>% data.matrix(),
                     s = ae.cv.fit$lambda.min)  # selecting minimum lambda

# Calculating R-squared
ae.sst <- sum((ae.test$AE - mean(ae.training$AE))^2)    #Sum of Squares Total
ae.sse <- sum((ae.pred.y - ae.test$AE)^2)           #Sum of Squares Error
ae.rsq <- 1 - ae.sse / ae.sst                       #R squared
ae.rsq 



# Extracting the beta coefficients contained in the model
ae.betas <- as.data.frame(as.matrix(coef(ae.cv.fit, 
                                         s = ae.cv.fit$lambda.min))) %>% tibble::rownames_to_column("Feature")
# Correlation between predicted vs. actual
cor.test(ae.test$AE, ae.pred.y)

```


#Recursive Shuffling function for permutation testing

```{r}

shuffler <- function(original_data, model, test_data, rep_num, seed, lambda, result, var){
  
    if(rep_num == 0){return(result)}
  
    else
      {set.seed(seed)
        
        I <- original_data
        
        if(var == "early") {
          
        # sample each column randomly to create shuffled variables, and performing data modifications as shown previously
        shuff_var_data <- I %>% mutate(mousetype = sample(I$mousetype),
                                       sex = sample(I$sex),
                                       Handedness = sample(I$Handedness),
                                       racialorigin = sample(I$racialorigin),
                                       major = sample(I$major),
                                       browsertype = sample(I$browsertype),
                                       EA = sample(I$EA),
                                       Age = sample(I$Age), 
                                       Sleep = sample(I$Sleep), 
                                       ComputerUsage = sample(I$ComputerUsage),
                                       education = sample(I$education),
                                       rating = sample(I$rating),
                                       clumsy = sample(I$clumsy),
                                       videogames = sample(I$videogames),
                                       RT_mean_baseline = sample(I$RT_mean_baseline),
                                       MT_mean_baseline = sample(I$MT_mean_baseline),
                                       ST_mean_baseline = sample(I$ST_mean_baseline),
                                       Var_sum_baseline = sample(I$Var_sum_baseline),
                                       screensize = sample(I$screensize)) %>% 
          
          dummy_cols(select_columns = c("mousetype",
                                        "sex",
                                        "Handedness",
                                        "racialorigin",
                                        "major",
                                        "browsertype"),
                     remove_selected_columns = TRUE) %>%
          
          mutate_at( c("EA",
                       "Age",
                       "Sleep",
                       "ComputerUsage",
                       "education",
                       "rating",
                       "clumsy",
                       "videogames",
                       "RT_mean_baseline",
                       "MT_mean_baseline",
                       "ST_mean_baseline",
                       "Var_sum_baseline",
                       "screensize"), scale) %>%
          
  dplyr::rename(racialorigin_african_american = 'racialorigin_african-american',
                racialorigin_indian_native = 'racialorigin_indian/native',
                racialorigin_pacific_islander = 'racialorigin_pacific-islander')%>% 
          
      filter(Subject.ID %in% test_data$Subject.ID)
       
      # Perform model building and r-squared calculations as previously shown                                         
      prediction <- predict(model, 
                           newx = shuff_var_data%>%select(-starts_with("Subject.ID"), -EA)%>%data.matrix(), 
                           s = lambda)
      
      sst <- sum((shuff_var_data$EA - mean(shuff_var_data$EA))^2)    #Sum of Squares Total and Error
      sse <- sum((prediction - shuff_var_data$EA)^2)
      rsq <- 1 - sse / sst 
       
      result[nrow(result) + 1,] <- rsq
      rep_num <- rep_num - 1
      seeds_left <- seed + 1
      
      return(shuffler(original_data, model, test_data, rep_num, seeds_left, lambda, result, var))
      
        }
        
        if(var == "late") {
          
        # sample each column randomly to create shuffled variables and performing data modifications as shown previously
        shuff_var_data <- I %>% mutate(mousetype = sample(I$mousetype),
                                       sex = sample(I$sex),
                                       Handedness = sample(I$Handedness),
                                       racialorigin = sample(I$racialorigin),
                                       major = sample(I$major),
                                       browsertype = sample(I$browsertype),
                                       LA = sample(I$LA),
                                       Age = sample(I$Age), 
                                       Sleep = sample(I$Sleep), 
                                       ComputerUsage = sample(I$ComputerUsage),
                                       education = sample(I$education),
                                       rating = sample(I$rating),
                                       clumsy = sample(I$clumsy),
                                       videogames = sample(I$videogames),
                                       RT_mean_baseline = sample(I$RT_mean_baseline),
                                       MT_mean_baseline = sample(I$MT_mean_baseline),
                                       ST_mean_baseline = sample(I$ST_mean_baseline),
                                       Var_sum_baseline = sample(I$Var_sum_baseline),
                                       screensize = sample(I$screensize)) %>% 
          
          dummy_cols(select_columns = c("mousetype",
                                        "sex",
                                        "Handedness",
                                        "racialorigin",
                                        "major",
                                        "browsertype"),
                     remove_selected_columns = TRUE) %>%
          
          mutate_at( c("LA",
                       "Age",
                       "Sleep",
                       "ComputerUsage",
                       "education",
                       "rating",
                       "clumsy",
                       "videogames",
                       "RT_mean_baseline",
                       "MT_mean_baseline",
                       "ST_mean_baseline",
                       "Var_sum_baseline",
                       "screensize"), scale) %>%
          
  dplyr::rename(racialorigin_african_american = 'racialorigin_african-american',
                racialorigin_indian_native = 'racialorigin_indian/native',
                racialorigin_pacific_islander = 'racialorigin_pacific-islander')%>% 
          
      filter(Subject.ID %in% test_data$Subject.ID)
      
      # Perform model building and r-squared calculations as previously shown                                             
      prediction <- predict(model, 
                           newx = shuff_var_data%>%select(-starts_with("Subject.ID"), -LA)%>%data.matrix(), 
                           s = lambda)
      
      sst <- sum((shuff_var_data$LA - mean(shuff_var_data$LA))^2)    #Sum of Squares Total and Error
      sse <- sum((prediction - shuff_var_data$LA)^2)
      rsq <- 1 - sse / sst 
       
      result[nrow(result) + 1,] <- rsq
      rep_num <- rep_num - 1
      seeds_left <- seed + 1
      
      return(shuffler(original_data, model, test_data, rep_num, seeds_left, lambda, result, var))
      
      }
        
        if(var == "ae") {
          
        # sample each column randomly to create shuffled variables and performing data modifications as shown previously
        shuff_var_data <- I %>% mutate(mousetype = sample(I$mousetype),
                                       sex = sample(I$sex),
                                       Handedness = sample(I$Handedness),
                                       racialorigin = sample(I$racialorigin),
                                       major = sample(I$major),
                                       browsertype = sample(I$browsertype),
                                       AE = sample(I$AE),
                                       Age = sample(I$Age), 
                                       Sleep = sample(I$Sleep), 
                                       ComputerUsage = sample(I$ComputerUsage),
                                       education = sample(I$education),
                                       rating = sample(I$rating),
                                       clumsy = sample(I$clumsy),
                                       videogames = sample(I$videogames),
                                       RT_mean_baseline = sample(I$RT_mean_baseline),
                                       MT_mean_baseline = sample(I$MT_mean_baseline),
                                       ST_mean_baseline = sample(I$ST_mean_baseline),
                                       Var_sum_baseline = sample(I$Var_sum_baseline),
                                       screensize = sample(I$screensize)) %>% 
          
          dummy_cols(select_columns = c("mousetype",
                                        "sex",
                                        "Handedness",
                                        "racialorigin",
                                        "major",
                                        "browsertype"),
                     remove_selected_columns = TRUE) %>%
          
          mutate_at( c("AE",
                       "Age",
                       "Sleep",
                       "ComputerUsage",
                       "education",
                       "rating",
                       "clumsy",
                       "videogames",
                       "RT_mean_baseline",
                       "MT_mean_baseline",
                       "ST_mean_baseline",
                       "Var_sum_baseline",
                       "screensize"), scale) %>%
          
  dplyr::rename(racialorigin_african_american = 'racialorigin_african-american',
                racialorigin_indian_native = 'racialorigin_indian/native',
                racialorigin_pacific_islander = 'racialorigin_pacific-islander')%>% 
          
      filter(Subject.ID %in% test_data$Subject.ID)
      
      # Perform model building and r-squared calculations as previously shown                                             
      prediction <- predict(model, 
                           newx = shuff_var_data%>%select(-starts_with("Subject.ID"), -AE)%>%data.matrix(), 
                           s = lambda)
      
      sst <- sum((shuff_var_data$AE - mean(shuff_var_data$AE))^2)    #Sum of Squares Total and Error
      sse <- sum((prediction - shuff_var_data$AE)^2)
      rsq <- 1 - sse / sst 
       
      result[nrow(result) + 1,] <- rsq
      rep_num <- rep_num - 1
      seeds_left <- seed + 1
      
      return(shuffler(original_data, model, test_data, rep_num, seeds_left, lambda, result, var))
      
        }
    }
}

```


#1000x Shuffler using group LASSO models

```{r}

early.noise <- shuffler(early.data.w.demo,
                        early.cv.fit$gglasso.fit,
                        early.test,
                        1000,
                        123,
                        early.cv.fit$lambda.min, 
                        data.frame(123), # dummy dataframe
                        "early") %>% filter(X123 != 123,)

late.noise <- shuffler(late.data.w.demo,
                       late.cv.fit$gglasso.fit,
                       late.test,
                       1000,
                       123,
                       late.cv.fit$lambda.min,
                       data.frame(123), # dummy dataframe
                       "late") %>% filter(X123 != 123)

ae.noise <- shuffler(ae.data.w.demo,
                     ae.cv.fit$gglasso.fit,
                     ae.test,
                     1000,
                     123,
                     ae.cv.fit$lambda.min, 
                     data.frame(123), # dummy dataframe
                     "ae") %>% filter(X123 != 123)
 
# Save re-sampled data
write.csv(early.noise,'early_1000_resamples.csv')
write.csv(late.noise,'late_1000_resamples.csv')
write.csv(ae.noise,'ae_1000_resamples.csv')

```


#Permutation plots against actual model performance

```{r}

early.noise %>% ggplot(aes(x=X123))+
  geom_boxplot()+
  geom_vline(xintercept = early.rsq, color = 'red') + 
  labs(x= 'R by chance') +
  theme_minimal()

late.noise %>% ggplot(aes(x=X123))+
  geom_boxplot()+
  geom_vline(xintercept = late.rsq, color = 'red') + 
  labs(x= 'R by chance') +
  theme_minimal()

ae.noise %>% ggplot(aes(x=X123))+
  geom_boxplot()+
  geom_vline(xintercept = ae.rsq, color = 'red') + 
  labs(x= 'R by chance') +
  theme_minimal()

```


#Beta Figures

```{r}

colnames(early.betas) <- c('Feature', 'Early')
early.betas <- early.betas %>% filter( 'Feature' != '(Intercept)')

colnames(late.betas) <- c('Feature', 'Late')
late.betas <- late.betas %>% filter( 'Feature' != '(Intercept)')

colnames(ae.betas) <- c('Feature', 'After_effect')
ae.betas <- ae.betas %>% filter( 'Feature' != '(Intercept)')

all.betas <- Reduce(function(x,y) merge(x,y,by="Feature", all=TRUE), list(early.betas, late.betas, ae.betas)) %>% 
  filter(Feature != "(Intercept)")

all.betas[,-1] <- round(all.betas[,-1], 2)

all.betas.w.labels <- all.betas %>%
  mutate(
    lab = c(
      "Age",
      "Browser: Chrome",
      "Browser: Edge",
      "Browser: FireFox",
      "Browser: Not Detected",
      "Browser: Opera",
      "Browser: Safari",
      "Cardinal",
      "CCW",
      "Clumsy",
      "Computer",
      "Education",
      "Hand: Ambi.",
      "Hand: Left",
      "Hand: Right",
      "Major: Arts",
      "Major: Business",
      "Major: Other",
      "Major: Psych.",
      "Major: Social sci.",
      "Major: Stem",
      "Mouse: Optical",
      "Mouse: Other",
      "Mouse: Track",
      "Movement Time Mean",
      "Neurological Disease",
      "Race: African-American",
      "Race: Asian",
      "Race: Indian Native",
      "Race: Latinx",
      "Race: Multiple",
      "Race: Other",
      "Race: Pacific Islander",
      "Race: White",
      "Rating",
      "Reaction Time Mean",
      "Screen Size",
      "Sex: Female",
      "Sex: Male",
      "Sex: Other",
      "Sleep",
      "Start Time Mean",
      "Variability",
      "Video Games",
      "Vision"
    )
  ) %>%
  
  mutate(shape_E = case_when(Early < 0 ~ '1',
                             TRUE ~ '0')) %>%
  mutate(shape_L = case_when(Late < 0 ~ '1',
                             TRUE ~ '0')) %>%
  mutate(shape_A = case_when(After_effect < 0 ~ '1',
                             TRUE ~ '0'))

early.late.beta.plot <- ggplot(all.betas.w.labels,
                               aes(
                                 x = abs(Early),
                                 y = factor(reorder(lab, abs(Late))),
                                 shape = shape_E
                               )) +
  geom_vline(aes(xintercept = 0),
             alpha = .7,
             color = 'light grey') +
  geom_point(size = 2.5,
             alpha = .7,
             color = 'blueviolet') +
  geom_point(
    size = 2.5,
    aes(
      x = abs(Late),
      y = reorder(lab, Late),
      shape = shape_L
    ),
    alpha = .7,
    color = 'firebrick2'
  ) +
  theme(
    axis.text.x = element_text(size = 12, hjust = 0.95),
    axis.text.y = element_text(size = 12, hjust = 0.95),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_blank(),
    axis.line = element_line(colour = "black"),
    legend.position = 'none'
  ) +
  scale_x_continuous(limits = c(0, .20)) +
  scale_shape_manual(values = c(1, 10), guide = FALSE)
early.late.beta.plot


ae.beta.plot <- ggplot(all.betas.w.labels,
                       aes(
                         x = abs(After_effect),
                         y = factor(reorder(lab, abs(After_effect))),
                         shape = shape_A
                       )) +
  geom_vline(aes(xintercept = 0), alpha = .7, color = 'light grey') +
  geom_point(size = 2.5, alpha = .7) +
  theme(
    axis.text.x = element_text(size = 12, hjust = 0.95),
    axis.text.y = element_text(size = 12, hjust = 0.95),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_blank(),
    axis.line = element_line(colour = "black"),
    legend.position = 'none'
  ) +
  scale_x_continuous(limits = c(0, .4)) +
  scale_shape_manual(values = c(1, 10), guide = FALSE)
ae.beta.plot

```


#Age and Adaptation

```{r}

my.phase <- ft.data %>%
  mutate(phase = case_when(
    TN >= 31 & TN <= 41 ~ "Early",
    TN >= 75 & TN <= 84 ~ "Late",
    TN >= 85 & TN <= 90 ~ "After"
  ))
my_phase_sum <- my.phase %>%
  group_by(SN, phase, Age) %>%
  dplyr::summarise(Hand_mean = mean(HandFlip, na.rm = TRUE),
                   RT_mean = mean(RT, na.rm = TRUE)) %>%
  drop_na()

my_phase_sum$phase <-
  factor(my_phase_sum$phase, levels = c("Early", "Late", "After"))

age_plot <- my_phase_sum %>%
  filter(Age < 85 ) %>%
  mutate(Age = round(Age / 10) * 10, GroupingVar = 1) %>%
  ggplot(aes(x = Age, y = Hand_mean)) +
  geom_pointrange(
    stat = "summary",
    fun.ymin = min,
    fun.ymax = max,
    fun.y = mean,
    size = .4
  ) +
  stat_summary(fun = "mean", geom = "line", aes(group = GroupingVar)) +
  scale_y_continuous(breaks = seq(-45, 45, 15)) +
  facet_rep_wrap(. ~ phase, ncol = 2, repeat.tick.labels = TRUE) +
  scale_x_continuous(breaks = seq(10, 90, 10)) +
  labs(x = "Age", y = "Hand Angle (°)", title = "") +
  scale_y_continuous(breaks = seq(0, 45, 5)) +
  coord_capped_cart(ylim = c(10, 45)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 0.95)) +
  theme_classic()
print(age_plot)

my_phase_sum %>%
  filter(Age < 85 & phase == "Late") %>%
  ggplot(aes(x = Age, y = Hand_mean)) +
  geom_pointrange(
    stat = "summary",
    fun.ymin = min,
    fun.ymax = max,
    fun.y = mean,
    size = .4
  ) +
  geom_smooth()



```
